---
title: "AniRevo Artist Alley System: Should there be change?"
author: "Naphyla"
format:
  html:
    code-fold: true
    code-summary: "Show Code"
---

## Why was this created?

The original survey was created to better understand how artists feel about the current format of artist alley participant selection. It has become increasingly difficult to be able to table at AniRevo, especially for local and new artists, under a first come first serve (FCFS) model.

Note: Neither the survey nor the analysis is affiliated with AniRevo in any way. This form is made by an artist to try and understand artists' needs

```{r}
#| echo: false
#| warning: false

# load libraries
if (!require("pacman")) {
  install.packages("pacman")
  library(pacman)
} 

p_load(
  googlesheets4, gargle,
  tidyverse,
  flextable
)

# load file
source("helper_functions.R")
all_gsheets <-gs4_find() # append all google sheets to an object

# preprocessing
df <- all_gsheets |> 
  filter(name == "AniRevo Artist Alley Format Survey (Responses)") |> 
  pull(id) |> 
  read_sheet(sheet = 1) |> 
  mutate(
    year_since_attandence = 2025 - `If yes, what was the most recent year that you boothed at AniRevo? (e.g., 2019)\n\nIf you have never boothed at AniRevo before, please put down 0`,
    year_since_attandence = na_if(year_since_attandence, 2025),
    table_2025 = ifelse(`Were you able to successfully purchase a booth during the most recent drop?` %in% c("Yes", "No, I already have a table from rebooking from last year"), "Secured Table", "Did Not Secure Table")
  )

```

## Respondant Demographics

The majority of respondents reside within the greater Vancouver area.

```{r}
df |> 
  mutate(`What geographical region do you live in?` = fct_relevel(
    `What geographical region do you live in?`,
    c("Another Canadian province",
      "Outside of the Greater Vancouver Area but within BC",
      "Greater Vancouver Area"))) |> 
      bar_graph(`What geographical region do you live in?`, "Set3")
```


## Past Attendance

About half of respondants have not tabled at AniRevo or not able to in the past.

```{r}
df |> 
  bar_graph(`Have you ever attended AniRevo as an artist in the past?`, "Pastel1")
```

For those who did table before, about half of them tabled last year.

```{r}
df |> 
  group_by(year_since_attandence) |> 
  summarise(`Number of respondants` = n()) |> 
  rename(`How many years has it been since you last tabled at AniRevo?` = year_since_attandence) |> 
  ungroup() |> 
  mutate(`%` = round(`Number of respondants`/ sum(`Number of respondants`) * 100, 2)) |> 
  flextable() |> 
  colformat_double(na_str = "NA", nan_str = "NaN") |> 
  autofit()
  

```

**Note:** `NA` means that the respondant has never tabled at AniRevo in the past.


Overall, we can see that roughly half of the respondents were able to secure a table for 2025 either through the drop or from rebooking. 

```{r}
df |> 
  bar_graph(`Were you able to successfully purchase a booth during the most recent drop?`, "Set3") + 
  labs(fill = "Were you able to successfully purchase\na booth during the most recent drop?")
```

## Opinions on the Current Artist Alley Format at AniRevo

The vast majority of artists would like the current process to be changed. 

```{r}
df |> 
  bar_graph(`Do you think AniRevo should change their current FCFS model?`, "Pastel1")
```

Importantly, artists, **regardless of whether they secured a table for 2025** think the current FCFS model should be changed

```{r}
df |> 
  grouped_bar_braph(`Do you think AniRevo should change their current FCFS model?`, table_2025, "Pastel1")
```

Most respondents expressed a desire to rebook their table if given the opportunity 

```{r}
df |> 
  bar_graph(`Do you think AniRevo should offer table rebooking for potential returning artists?`, "Pastel1")
```

However, there is a much bigger discrepancy between artists who did manage to secure a table versus those who do not. 

Based on artists' responses in the comment section, there is a clear desire for *stability and security*. This may also be a symptom reflecting the uncertainty that comes with a FCFS model: if artists do manage to secure a table, given how difficult it would be to return if they were to give it up, they would be even more likely to want an opportunity to rebook a table for next year.

```{r}
df |> 
  grouped_bar_braph(`Do you think AniRevo should offer table rebooking for potential returning artists?`, table_2025, "Pastel1")
```

### What new format would artists want to see at AniRevo?













